An Evolutionary Algorithm for the Multiobjective Risk-Equity Constrained Routing Problem

### 2011-11-10 trunk/DAW_hazmatHypE/trunk/paper/hazmatRouting_EvolOptim.tex
added figures comparing the two initialization schemes

>>>>

\subsection{Random Initialization Versus Cost-Optimal Initialization}

\begin{figure}%
	\includegraphics[width=\columnwidth]{../experiments/randVsCost/allsolutions.eps}%
	\caption{\label{fig:allsolutions} Comparison between the random initialization (circles) and the cost-optimal one (crosses). Shown are the populations of 10 independent HypE runs after 1000 generations for all three objectives (top left) and each combination of two objectives.}
\end{figure}

\begin{figure}%
	\includegraphics[width=\columnwidth]{../experiments/randVsCost/onlynondominated.eps}%
	\caption{\label{fig:onlynondominated} Comparison between the random initialization (circles) and the cost-optimal one (crosses). Shown are only the non-dominated solutions in the final populations of 10 independent HypE runs after 1000 generations.}
\end{figure}

\subsection{Comparison With An Exact Algorithm for the Two Linear Objectives}
\TODO{add plots and describe what we compare (efficient cost/risk paths multiplied by the number of trucks); result: EA is better}
